Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-16 ms.tex
added some more details to Kepler analysis

We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
\begin{equation}
A = \frac{(f - 1) \bullet a}{a \bullet a},
\end{equation}
where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.
This dot product is then multiplied by the average transit light curve to create a 2D model grid.
The residual of this model shows substantial deviations from white noise, so we explore more sophisticated models than the average light curve below.

@@

We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$-0.12 to $\sim$0.15).
\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit using 4 Principal Components (Top Right).
(Right) The residuals show smaller residuals than the average model.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
\caption{(Left) Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical noise.
(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histograms}
\end{centering}
\end{figure*}

>>>>

We start by taking the average transit light curve of all the long cadence data (the mean of the 2D grid along the transit number axis).
We then take the dot product ($\bullet$) with this average light curve to create an amplitude time series.
\begin{equation}
A = \frac{(f - 1) \bullet a}{a \bullet a},
\end{equation}
where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $a$ is the average spectrum.

This dot product is then multiplied by the average transit light curve to create a 2D model grid.
The residual of this model (Figure \ref{fig:riverPlots}) shows significant $\pm$0.2\% deviations from white noise, indicating that the dusty tail surrounding \sha\ shanges in shape with time.
We explore more sophisticated models than the average light curve below that are based on principal component analysis.
However, this average model serves as a useful comparison to fitting lower-precision photometry, such as the ground-based light curves typical photometric scatter is $\sim$ 0.1 to 0.2\% for 20 minute timescales.

@@

We use a covariance matrix as opposed to correlation matrix to calculate the principal component eigenvectors.
In other uses of PCA, the variables are often scaled so that they all have a variance of 1.0 to ensure that variables with intrinsically larger variance (such as height in inches over weight in kilograms) do not get higher loadings in the principal component vectors \citep{jolliffe2002pca}.
However, we do not scale the variables (columns) by variance and use a covariance matrix because all of our variables are the same units, flux.
If we scaled each column in this 2D grid by its standard deviation or used a correlation matrix, this would magnify the contribution of photon noise to out-of-transit data over the real astrophysical variability of the inner phases (between $\sim$ -0.12 to $\sim$0.15).
\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.32\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_model_2D.pdf}
\includegraphics[width=0.32\textwidth]{images/kepler/pca_resid_2D.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit using 4 Principal Components (Middle).
The residuals (Right) have $\lesssim 0.1\%$ residuals in contrast to the average-light curve method used in Figure \ref{fig:riverPlots}.
}\label{fig:riverPlotsPCA}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_periodogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc2_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:tserPC1}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with \citet{kawahara2013starspots}, who notice that this period is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\caption{(Left) Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the statistical photon noise that explains shy some transit depths appear less than 0.
}\label{fig:histograms}
\end{centering}
\end{figure*}
